---
title: "EPI 590 Final"
format: html
---
This data presents information on the 2022 World Cup predictions made by FiveThirtyEight. This data allowed them to make predictions on which teams would advance from the group stage using metrics like expected goals and Soccer Power Index.
```{r}
#| echo: false
#| message: false
here::here("data","wc_matches.csv")

matches <- read.csv(here::here("data", "wc_matches.csv"))

library(gtsummary)
library(dplyr)


matches <- rename(matches, home = team1, away = team2)
matches <- matches %>% mutate(winner = ifelse( score1 > score2, 1, 0))
```
```{r}
#| echo: false
#| label: tbl-one
#| tbl-cap: "Descriptive statistics"
#| output-location: slide
table1 <- tbl_summary(
	matches,
	include = c(prob1, prob2, xg1, xg2, spi1, spi2),
	label = list(
		prob1 ~ "Probability of Home Win",
		prob2 ~ "Probability of Away Win",
		xg1 ~ "Home Team Expected Goals",
		xg2 ~ "Away Team Expected Goals",
		spi1 ~ "Home Team Soccer Power Index",
		spi2 ~ "Away Team Soccer Power Index"
	))
table1
```
@tbl-one contains descriptive statistics on the 64 games played. 
```{r}
#| echo: false
regression <- tbl_uvregression(
	matches,
	y = winner,
	include = c(prob1, prob2, xg1, xg2, spi1, spi2),
						method =glm)
inline_text(regression, variable = "prob1")
```

```{r}
#| echo: false
expected_goals <- matches$xg2
```
```{r}
#| echo: false
#| label: fig-hist
#| fig-cap: "Away Team Expected Goals"
hist1 <- hist(expected_goals)
```
```{r}
#| echo: false
stats <- list(n = nrow(matches),
							mean_xg = mean(matches$xg2))
```
@fig-hist shows a distribution of the expected goals for away teams.
Among the away teams, there were `r stats$n` teams and an average of `r stats$mean_xg` expected goals. 
